%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
%% TeamX INC
\cventry
{Backend Software Developer~~~路~~~8 months co-op~~~路~~~Outstanding} % Job title
{TeamX Inc.} % Organization
{Kitchener, ON, Canada} % Location
{May. 2018 - Dec. 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Implemented a microservice in Scala to do realtime ranking and prioritization of content.}
		\item {Optimized developer workflow, automated production builds using CI (CircleCI).}
		\item {Introduced and implemented back-end push notification support, implemented a push notification generator.}
		\item {Implemented log collection across back-end microservices to facilitate easier debugging.}
	\end{cvitems}
}

%---------------------------------------------------------
%% RAVE INC
\cventry
{Backend Software Developer~~~路~~~8 months co-op~~~路~~~Outstanding} % Job title
{Rave Inc.} % Organization
{Kitchener, ON, Canada} % Location
{Jan. 2017 - Aug. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Expanded RESTful API server to provide support for multitude of new features (such as additional video providers - Netflix and Viki) for the app.}
		\item {Developed, built and deployed microservice infrastructure in Scala and Clojure utilizing Docker, CircleCI, Kubernetes, and GCloud stack (Kubernetes Engine (formerly Container Engine), Container Registry, Pub/Sub, Compute Engine,  Buckets, Stackdriver), focusing on high-availability and fault tolerance.}
		\item {Redeveloped the logic behind sending push notifications to iOS devices to prevent lost push notifications and incorrect badge counts.}
		\item {Assisted teams in utilizing Graylog (a solution for analyzing and storing logs) for their microservices.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Administrator} % Job title
{Proficinema} % Organization
{Moscow, Russian Federation} % Location
{Jun. 2014 - Dec. 2014} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Assisted in system administration of Linux servers.}
		\item {Provided general IT support.}
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Start-Polus LLC.} % Organization
    {Moscow, Russian Federation} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesigned and updated corporate website.}
        \item {Implemented web-based order forms.}
        \item {Optimized contents of the website in order to be ranked higher in Google/Yandex search results.}
      \end{cvitems}
    }
\end{cventries}
